### 2021-05-03 thesis/tex/nsiTheory.tex
update

\section{Non-standard interactions in IceCube}
In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$ directly or 
indirectly. Since all standard matter potentials are diagonal, the elements $\epsilon{\a\a}$ will directly adjust the matter potential felt 
by flavor $\a$. The off-diagonal terms have a more interesting implication. %TODO: fill
In Fig.~\ref{fig:IC_NSI_probs}, we plot $\Pmm$ and $\Pamam$ for 3 cases of $\ep$ and $\emt$ each. As is clear from the 
left panels, the value of $\ett$ does not affect neither $\Pmm$ nor $\Pamam$, as we expected. Hence, we will not be able
to say anything about $\ett$ in our study. The right panels show an interesting relationship between the sign of the NSI parameter 
and the neutrino type. $\Pmm$ with positive $\ett$ is the same as $\Pamam$ with negative $\ett$. Looking at the form of the matter potential, 
this is something that we should expect. In the standard interaction framework, we distinguish between neutrinos and antineutrinos by flipping the sign 
of the CC potential. Since the NSI potential has the same form, any sign flipping of the NSI potential will have the same effect as 
having an antineutrino.

>>>>

\section{Non-standard interactions in IceCube}
In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$ directly or 
indirectly. Since all standard matter potentials are diagonal, the elements $\epsilon_{\a\b}, \a = \b$ will directly adjust the matter potential felt 
by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as the open up matter interactions across flavors. Remember, in the Standard model,
we are restriced to weak interactions that conserve lepton number. However, a off-diagonal NSI parameter allows flavor transitions during matter interactions.
Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
of the mixing matrix. Thus, we can in theory boost a flavor transition which is supressed by the mixing matrix. Moreover, since the NSI parameters are 6, and the PMNS
matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix.

As discussed in Eq.~\ref{eq:Uvalues}, the atmospheric $\nm \to \nt$ transition will be the most abundant, making $\emt$ and $\emm$ or $\ett$ the most suitable
NSI parameters to constrain.

In Fig.~\ref{fig:IC_NSI_probs}, we plot $\Pmm$ and $\Pamam$ for 3 cases of $\ep$ and $\emt$ each. As is clear from the 
left panels, the value of $\ett$ does not affect neither $\Pmm$ nor $\Pamam$, as we expected. Hence, we will not be able
to say anything about $\ett$ in our study. The right panels show an interesting relationship between the sign of the NSI parameter 
and the neutrino type. $\Pmm$ with positive $\ett$ is the same as $\Pamam$ with negative $\ett$. Looking at the form of the matter potential, 
this is something that we should expect. In the standard interaction framework, we distinguish between neutrinos and antineutrinos by flipping the sign 
of the CC potential. Since the NSI potential has the same form, any sign flipping of the NSI potential will have the same effect as 
having an antineutrino.

### 2021-05-03 thesis/tex/oscillations.tex
update

>>>>

In this work, we will be using the best-fit values from~\cite{nufit},
\begin{align}\label{eq:nufitparams}
    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \Delta m^2_{31} =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
\end{align}
with the exception of the CP-violating phase $\delta_\text{CP}$ which we always set to zero for simplicity. The PMNS matrix then has the numerical values 
\begin{align}\label{eq:Uvalues}
    U = \begin{pmatrix}
        U_{e e} & U_{e\mu} & U_{e\tau} \\
        U_{\mu e} & U_{\mu \mu} & U_{\mu \tau} \\
        U_{\tau e} & U_{\tau \mu} & U_{\tau \tau}
    \end{pmatrix} 
    = \begin{pmatrix}
        0.825 & 0.545 & 0.149 \\
        -0.455 & 0.485 & 0.746 \\
        0.334 & -0.684 & 0.649
    \end{pmatrix} \,.
\end{align}
In our study, we will only use atmospheric neutrinos, of which $\nm$ are the most abundant. We see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
suggesting that $\nm$ primarily oscillates into $\nt$, at least in vacuum. We will see that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
the most abundant. This means we will be able to constrain any parameters relating to $\nm \to \nt$ oscillations stringently.
